---
title: "Instructions Zenodo - download all"
author: "Ivan Calandra"
date: "`r Sys.time()`"
output:
  github_document: 
    toc: true
    toc_depth: 2
    html_preview: false
---

```{r Knitr Options, include = FALSE}
knitr::opts_chunk$set(comment = NA, message = FALSE, indent = "", error = TRUE, eval = FALSE)
```


# Purpose
This document details the steps to download all the files from a given Zenodo record, either using R or Python.

Note that the code is there only to show the steps taken to download the file and is therefore not evaluated (`knitr::opts_chunk$set(eval=FALSE)`).

---


# R instructions
These instructions use the package [`zen4R`](https://github.com/eblondel/zen4R) by Emmanuel Blondel.

## Installation
```{r}
library(devtools)
install_github("eblondel/zen4R")
```

## Running
```{r}
library(zen4R)
download_zenodo("Zenodo_doi", path = "target_directory")
```

## Simple example
```{r}
download_zenodo("10.5281/zenodo.3632517", path = "D:/Zenodo")
```

## More practical example
```{r}
doi <- "10.5281/zenodo.3632517"
target_folder <- paste0("D:/Zenodo/", basename(doi))
dir.create(target_folder)
download_zenodo(doi, path = target_folder)
```


---


# Python instructions
These instructions use the package [`zenodo_get`](https://github.com/dvolgyes/zenodo_get/tree/v1.3.0) by David Völgyes.  
It requires [Python](https://www.python.org/) 3 to work.  

These instructions are for Windows 10. Linux and Mac users will hopefully be able to adapt them themselves. 

All of these commands are to be run in the Windows PowerShell (press the "Windows" key or click on the "Start" icon, and type "powershell" to open it).

## Installation
```
python -m pip install zenodo_get --user
```

## Running
```
chdir target_directory
python -m zenodo_get Zenodo_doi -m -e -k
```

## Example
```
mkdir D:\Zenodo\zenodo.3632517
chdir D:\Zenodo\zenodo.3632517
python -m zenodo_get 10.5281/zenodo.3632517 -m -e -k
```



